### 2015-12-02 paper.tex
Describe how steady duration is found

For each tow, a relevant quasi-steady duration was selected \textbf{\textit{[need a discussion on how this is done and justified]}}, and then truncated
to include a whole number of blade passages. Over this duration relevant
statistics are calculated.

>>>>

For each tow speed, a relevant quasi-steady duration was selected by manually
inspecting a plot of the $C_P$ time series, and then truncated to include a
whole number of blade passages. Over this duration relevant statistics are
calculated.
